\TitleText

### 2020-03-24 presentation/1_introduction.tex
Update slides

\Title {\TitleText}
\Subtitle {II. Completing the Proof}
\blank [big]

@@

\page [yes]
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Organization}
{
\I Introduction

\I Problem Setting and Proposed Method

\I Proving the performance bound: Sparsity, Concentration Inequality, and Expected Error

\I Conclusion and Future Work

\I References
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Background}
{
\I Multiple-input-multiple-output (MIMO) wireless communication is expected to be the next-generation r\'egime.

\I But channel response has to be known at the receiver to facilitate such algorithms as beamforming and channel calibration.

\I It calls for high complexity to estimate MIMO channels.

\I Meanwhile, millimeter wave (mmWave) channels often exhibit sparse properties.

\I Under mmWave setting, if the sparsity is exploited, can few observations suffice to estimate the channel?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Compressive Sensing}
{
\I The situation that the number of model parameters is much larger than the number of measurements has been well studied, and and \Emph {compressed sensing} (CS) address exactly that.

\I The problem can be considered to be inverting a wide, rectangular matrix.
With insufficient (even noisy) measurements, this does not make sense.

\I But what if we impose other conditions?
Indeed, it turns out that, when the signal is sparse, few observations may be sufficient for the reconstruction.
And Dantzig Selector (DS), proposed by Cand\`es and Tao (2006) in the advent, is a possible solution.
}

>>>>

\Title {\TitleText}
\Subtitle {Numerical Experiments}
\blank [big]

@@

\page [yes]
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Organization}
{
\I Problem Setting

\I Proposed Method

\I Bound for the Error Norm

\I Numerical Experiments

\I Conclusion and References
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Background}
{
\I Multiple-input multiple-output (MIMO) communication system has been proposed as part of the 5G specification, but its hardware overhead increases complexity and power consumption.

\I The design of new algorithms addressing these issues requires channel information to be known.

\I Estimation of MIMO channels also results in high complexity, due to the large number of antennae.

\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit sparse properties, which we exploit to save for some measurements.
}

### 2020-03-24 presentation/2_setting.tex
Update slides

\I Consider the channel representation
\Disp {
\NC \M{H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB {\f_l'}
\V {a} \SB {\th_l'}^\Adj
\in \MB {C} ^{N_H \D N_H} \NR
}

@@

\I Under the assumption
\Disp {
\NC N_H \gg \NC N_R \gg N_Y \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Effective Channel}
{
\I Consider Complex Standard Normal \m {\M{Z} \in \NC \MB {C} ^{N_H \D N_H}}

\I Introduce the effective channel
\Disp {
\NC \M{Y}
:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
}

\I Summarizing the dimension,
\Disp {
\NC \MB {C}^{N_Y}
\underset {\M{F}_B} {\mapsto} \NC \MB {C}^{N_R}
\underset {\M{F}_R} {\mapsto} \MB {C}^{N_H}
\underset {\M{H}} {\mapsto} \MB {C}^{N_H}
\underset {\M{W}_R} {\mapsto} \MB {C}^{N_R}
\underset {\M{W}_B} {\mapsto} \MB {C}^{N_Y} \NR
}

\I How do we \Emph {recover} \m {\M {H}} with knowledge of \m {\M {Y}}?

\I How do we \Emph {design} \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Transform to the Angular Domain}
{
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {Z}} \NR
}

\I Then we have a \Emph {linear equation}
\Disp {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Proposed Method}
{
\I Input \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{N_H^2}}, \m{\g_{\Ss {DS}} \geq 0}.

>>>>

\I Consider the channel representation
\Disp {
\NC \m {H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB {\f_l'}
\V {a} \SB {\th_l'}^\Adj
\in \MB {C} ^{N_H \D N_H} \NR
}

@@

\I Under the assumption
\Disp {
\NC N_H \gg \NC N_R \gg N_Y \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Effective Channel}
{
\I Consider Complex Standard Normal \m {\m {Z} \in \NC \MB {C} ^{N_H \D N_H}}

\I Introduce the effective channel
\Disp {
\NC \m {Y}
:=\m {W}_B \m {W}_R \RB {\m {H} \m {F}_R \m {F}_B +\m {Z}} \NR
}

\I Their dimension is summarized for convenience:
\Disp {
\NC \MB {C}^{N_Y}
\underset {\m {F}_B} {\mapsto} \NC \MB {C}^{N_R}
\underset {\m {F}_R} {\mapsto} \MB {C}^{N_H}
\underset {\m {H}} {\mapsto} \MB {C}^{N_H}
\underset {\m {W}_R} {\mapsto} \MB {C}^{N_R}
\underset {\m {W}_B} {\mapsto} \MB {C}^{N_Y} \NR
}

\I Problem (a): How do we recover \m {\M {H}} with knowledge of \m {\M {Y}}?

\I Problem (b): How do we design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Transform to the Angular Domain}
{
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \m {K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {Z}} \NR
}

\I Then we have a linear equation
\Disp {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Compressive Sensing}
{
\I In our case, we have to essentially invert an underdetermined system, and usually, that is not well defined.

\I Consider a simpler case: \m {\V {y} = \M {A} \V {x} + \V {z}}, where \m {\M {A} \in \MB {R} ^{N_m \D N_p}}, \m {\V {y} \in \MB {C} ^{N_m}}.

\I If \m {\V {y} = \M {A} \V {x}_1 = \M {A} \V {x}_2}
\Disp {
\NC \V {x}_1 - \V {x}_2 \in \Rm {null}\; \M {A} \NR
}
Then \m {\V {x}_1, \V {x}_2} cannot be recovered.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Restricted Isometry Property}
{
\I However, Candès and Tao shows that when the signal is sparse, few measurements may be sufficient for the reconstruction, with vanishing error norm, in overwhelming probability.

\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.

\I We say that \m {\m {P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {g}} _2^2
\leq \NC \VNm {\m {P} \V {g}} _2^2
\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
}

\I Verbally, \m {\m {P}} is \Emph {almost unitary} up to relative error \m {\d_s}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Dantzig Selector for Sparse Vectors}
{
\I Let \m {\V {x}} be \m {S}-sparse.
If \m {\g_{\Ss {DS}} = \R {2 \log N_p}}, then
\Disp {
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}'}  \MC \VNm {\V {x}'} _1 \NR
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {A}^\intercal \RB {\V {y} -\M {A} \V {x}'}} _\infty \leq \g_{\Ss {DS}} \NR
\stopcases \NR
}
with
\Disp {
\NC \VNm {\V {x} - \hat {\V {x}}} _2 ^2
\leq \NC 32 S \sigma^2 \log N_p \NR
}
For high probability.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Proposed Method}
{
\I Back to our problem: Input \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.

### 2020-03-24 presentation/3_proof.tex
Update slides

\Frame {The Need of a Modified Proof}
{
\I \Emph {Q1}: DS is shown to work for \Emph {sparse} vectors, but is \m {\M {H}} really sparse?

\I \Emph{Q2}: Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but is it true for \m {\M {P}}, and under what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}?

\I \Emph{Q3}: Candès and Tao established the case for real matrices, but does \Emph {complex} case apply?

\I \Emph{Q4}: Candès and Tao showed the Big-\m {\MC {O}} of error norm depends on (in our case) \m {N_H}, but does the algorithm work successfully for \Emph {high probability}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Proof Strategy}
{
\I \m {\M {H}} is not sparse, but \m {\M {K}^\Adj \M {H} \M {K}} is.
Remove the largest-magnitude \m {S} components of \m {\V{g}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, so that it remains to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}}}.

\I Establish that \m {\M{W}_R} and \m {\M{W}_R} satisfies RIP, thus \m {\M{P}} satisfies RIP too, for high probability.

\I We then establish a modified bound of error norm based on Candès and Tao.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Restricted Isometry Property}
{
\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.

\I We say that \m {\M{P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {g}}^2
\leq \NC \VNm {\M{P} \V {g}} _2^2
\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
}

\I Verbally, \m {\M{P}} is \Emph {almost unitary} up to relative error \m {\d_s}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Suppose for concreteness,
\Disp {
\NC s
=\NC \R {\log N_H},
\Q S
= L s^2,
\Q \d_S
\leq \F {1} {8} \NR
}

@@

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I Considering \Emph {Q2}: If each entry of \m {\M {P}} is i.i.d., then it's likely that, by whatever variation of \Emph {Central Limit Theorem}, for unit vector \m {\V {u}}
\Disp {
\NC \MB {E} \SB {\VNm {\M {P} \V {u}} _2 ^k}
\approx \NC 1
\Q \Ss {in\; distribution} \NR
}

\I Unfortunately, they are \Emph {not i.i.d.}, and that need closer scrutiny.

\I Try to set each entry of \m {\M{F}_B} (resp.\ \m {\M{W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant

\I And let each entry of \m {\M{F}_R} (resp.\ \m {\M{W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Effective Beamformers}
{
\I Is it true that if \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has?

\I Indeed, if so, \m {\M {P}} has approximately \m {2\d_s}-RIP, if there is no sparsity constraint:
\Disp {
\NC \VNm {P} _2
=\NC \VNm {\M {F}_B^\Tr \M {F}_B^\Tr} \VNm {\M {W}_B \M {W}_R} \NR
}

\I I argue that this is true for sparse \m {\V {g}}.
In fact, if \m {\M {G} =\M {U} \Rm {diag} \SB {\V {d}} \M {U} ^\Adj}, for some \m {S}-sparse \m {\V {d}} and unitary \m {\M {U}}.

\Disp {
\NC \NC \VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} \M {U}
   \R {\Rm {abs} \SB {\V {d}}} \D
   \R {\Rm {abs} \SB {\V {d}}}
   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} \NR
%
\NC \eqsim \NC \VNm {\M {K} \M {H} \M {K} ^\Adj} _2 \RB {1 +2\d_s} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Digital Beamformers}
{
\I For \m {0 <\d_s <1}, unit vector \m {\V {u}}, \m {\M {W}_B} (resp.\ \m {\M {F} _B ^\Adj}) satisfies
%
\Disp {
\NC \Nm {\VNm {\M {W} _B \V {u}}^2 - 1}
\geq \NC \d_s \NR
}

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \Ss {e} ^{-N_B \R {\d_s} /4} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Analog Beamformers}
{
\I Suppose
%
\Disp {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
}
%
\I Then \m {\M {W}_R} (resp.\ \m {\M {F} _R ^\Adj}) has \m {\d_s}-RIP...

\I for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error Norm of Dantzig Selector}
{
\I In answer of \Emph {Q3}, it can be checked that the generalization to complex vectors only introduces the bound of a multiple \m {\R {2}}.

\I then the following bound holds for high probability:
\Disp {
\NC \VNm {\V {d}} _2
%
\leq \NC 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
}

}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Big-\m {O} of Success Probability (1/2)}
{
\I Denote the four events of failure, subscript respectively for restricted isometry, noise, sparsity,
\Disp {
\NC q
\eqsim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
}

\I Then previous discussions
\Disp {
\NC q _{\Rm {iso}, B}
\lesssim \NC 2 \Ss {e} ^{-N_B /12} \NR
%
\NC q _{\Rm {iso}, R}
\lesssim \NC 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
%
\NC q _{\Rm {no}}
\lesssim \NC N_H ^{-2} \NR
%
\NC q _{\Rm {sp}}
\lesssim \NC 2 \Ss {e} ^{-9L/\pi} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Big-\m {O} of Success Probability (2/2)}
{
\I If we provide the design values
\Disp {
\NC N_B
\gtrsim \NC 4 \log N_H \NR
%
\NC N_R
\gtrsim \NC 16 L \RB {\log N_H}^2 \NR
}

\I It follows that
\Disp {
\NC q _{\Rm {sp}}
\lesssim \NC q _{\Rm {no}}
\lesssim q _{\Rm {iso}, B}
\eqsim q _{\Rm {iso}, R}
}

\I Then we get the estimation
\Disp {
\NC q
\eqsim 2 N_H ^{-1/3} \NR
}
}

>>>>

\Frame {Modifying the Original Proof}
{
\I \Emph{Q1}: Candès and Tao established the case for real matrices, but does \Emph {complex} case apply?

\I \Emph {Q2}: DS works for \Emph {sparse} vectors, but as \m {\M {H}} is not sparse, does DS work?

\I \Emph{Q3}: DS requires the measurement matrix to have restricted isometry property, but under what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, is it true for \m {\M {P}}?

\I \Emph{Q4}: Candès and Tao showed the Big-\m {\MC {O}} of error norm depends on (in our case) \m {N_H}, but does the algorithm work successfully for \Emph {high probability}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Real Valued Representation}
{
\I To save complexity, we represent a complex number by its real- and imarinary-parts.

\I For vectors, substitute
\Disp {
\NC a +b \Ss{i}
\leftrightarrow \NC \startTheMatrix
\NC a \NR
\NC b \NR
\stopTheMatrix \NR
}

\I For matrices, substitute
\Disp {
\NC a +b \Ss{i}
\leftrightarrow \NC \startTheMatrix
\NC a, \NC -b \NR
\NC b, \NC a \NR
\stopTheMatrix \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %

\Frame {Observations on Sparsity}
{
\I \m {\M {H}} is not sparse, but \m {\M {K}^\Adj \M {H} \M {K}} is almost sparse.
Call the largest-magnitude \m {S} components of \m {\V{g}} to be \m {\M {g} _{\SB{\MC {A}}}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, we still have to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1}.

\I Establish that all four beamformers satisfy RIP, for high probability, thus \m {\m {P}} satisfies RIP too, for high probability.

\I We then establish a modified bound of error norm.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Suppose for concreteness,
\Disp {
\NC S
= L \log N_H,
\Q \d_S
\leq \F {1} {8} \NR
}

@@

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I I argue in the treatise that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has?

\I Try to set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant

\I And let each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Digital Beamformers}
{
\I For \m {0 <\d_s <1}, unit vector \m {\V {u}}, \m {\M {W}_B} (resp.\ \m {\M {F} _B ^\Adj}) satisfies
%
\Disp {
\NC \Nm {\VNm {\M {W} _B \V {u}} _2^2 - 1}
\geq \NC \d_s \NR
}

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \Ss {e} ^{-N_Y \R {\d_s} /4} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Analog Beamformers}
{
\I Suppose
%
\Disp {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
}
%
\I Then \m {\M {W}_R} (resp.\ \m {\M {F} _R ^\Adj}) has \m {\d_s}-RIP...

\I for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error Norm of Dantzig Selector}
{
\I The following bound holds for high probability \m {p}:
\Disp {
\NC \VNm {\Hat {\V {g}} - \V {g}} _2
%
\leq \NC 8 \R {L} \R {\log N_H}^3 \NR
}

\I where it hold for \m {p} that...
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Big-\m {O} of Success Probability}
{
\I Denote the four events of failure, subscript respectively for restricted isometry, noise, sparsity,
\Disp {
\NC q = 1-p
\lesssim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
}

\I If we provide the design values
\Disp {
\NC N_Y
\gtrsim \NC 4 \log N_H, \Q
N_R
\gtrsim 16 L \RB {\log N_H}^2 \NR
}

\I It follows that
\Disp {
\NC q _{\Rm {sp}}
\lesssim \NC q _{\Rm {no}}
\lesssim q _{\Rm {iso}, B}
\eqsim q _{\Rm {iso}, R} \NR
%
\NC q
\lesssim \NC 2 N_H ^{-1/3} \NR
}
}
